Combined Task and Motion Planner through an Interface Layer

### 2015-05-12 documentation/ps4.tex
modifying results table

\begin{figure}
\begin{tabular}[t]{|l|l|l|l|l|l|}
\hline
Shape & Blocks & obstructions & Motion Planner Calls & Task Planner Calls & runtime \\ \hline
Horizontal Line & 3 & 12 & ? & ? & ?\\
\hline
Vertical Line & 3 & 12 & ? & ? & ?\\
\hline
X & 5 & 8 & ? & ? & ?\\
\hline
Cross & 5 & 20 & ? & ? & ?\\
\hline
Square & 9 & 56 & ? & ? & ?\\
\hline

@@

>>>>

\begin{figure}
\begin{tabular}[t]{|l|l|l|l|l|l|l|}\extrarowheight
\hline

Shape & Blocks & \shortstack{Goal Number of\\Blocks to Move} & Obstructions & \shortstack{Motion Planner\\Calls} & \shortstack{Task Planner\\Calls} & Runtime \\ \hline
Square & 9 & 56 &  & ? & ?&\\
\hline
Sorting & 9 & 56 & ? & ? & ?&\\
\hline

@@

\section{Limitations}

\section{Optimizations}
